Response to Reviewers

### 2021-11-17 Scripts/Initial_Analysis.Rmd
Created splitted figure 3 for rev.2

SummaryProp(taxon_key)

@@

World_eez_sf <- st_read(my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile", "SAUEEZ_July2015.shp")) %>% 
  rename(eez_name = Name) %>% 
  st_transform(crs = 4326) %>% # 4326
  # st_transform(crs = "+proj=eck4") %>% # for tbular plot
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  clean_names()

@@

World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf")) %>%
  clean_names() %>% 
  select(iso_a3,sovereignt,sov_a3,name,name_long,region_wb,continent,geometry) %>% 
  # st_transform(crs = "+proj=eck4") %>%
  st_transform(crs = 4326) %>% # 4326
  mutate(iso_a3 = ifelse(sovereignt == "Norway","NOR",
                         ifelse(name == "France","FRA",
                                iso_a3)
                         )
         ) %>% 
    left_join(World_map_dat,
            by = "iso_a3")

@@

ggplot(Eez_centroid_sf) +
  geom_sf()

@@

@@

data_ready_plot <- data_ready_plot %>% 
  mutate(
    per_early_plot = ifelse(per_early_plot >= 50,50,per_early_plot),
    per_mid_plot = ifelse(per_mid_plot >= 50,50,per_mid_plot))

sf_ready_plot <- st_as_sf(data_ready_plot,
            coords = c("lon", "lat")
            ) %>% 
  st_set_crs(4326) %>% # to match shapefiles
  st_transform(crs = "+proj=eck4")

# Get arrow data
arrows_data <- as.data.frame(st_coordinates(st_cast(sf_ready_plot,"POINT")$geometry)) %>% 
  bind_cols(data_ready_plot)

# Get point data
point_data <- path_data %>% 
  filter(per_early <= 0) %>% 
  st_as_sf(
    coords = c("start_lon", "start_lat")
  ) %>% 
  select(source,target,geometry) %>% 
  st_set_crs(4326) %>% 
  st_transform(crs = "+proj=eck4")

@@

@@

# Plot
p <-
  ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
  geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
  geom_sf(data = subset(sf_ready_plot, per_early_plot >= 0), aes(color = per_early_plot), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
  my_ggtheme_m(leg_pos = "bottom") +
    geom_path(data = subset(arrows_data, per_early_plot >= 0),
              aes(X, Y,
                  group = group,
                  col = per_early_plot
              ),
              size = 1,
              arrow = arrow(length = unit(0.01, "npc"),
                            ends = "first"),
              show.legend = NA) +
  my_ggtheme_m(leg_pos = "bottom") +
  scale_color_gradientn(name= "Changes in catch proportion \nand changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(data_ready_plot$per_early_plot,na.rm=T)),
                        breaks = seq(0,max(data_ready_plot$per_early_plot,na.rm=T),10),
                        labels = c(seq(0,max(data_ready_plot$per_early_plot-10,na.rm=T),10),">50")
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion \nand changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(data_ready_plot$per_early_plot,na.rm=T)),
                        breaks = seq(0,max(data_ready_plot$per_early_plot,na.rm=T),10),
                        labels = c(seq(0,max(data_ready_plot$per_early_plot-10,na.rm=T),10),">50")
  )

ggsave(plot =  p,
       "./Figures/ssr_early.png",
       width = 10,
       height = 5,
       units = "in")

>>>>

# SummaryProp(taxon_key)

@@

World_eez_sf <- st_read(my_path("G", extra_path = "Spatial/SAU/SAU_Shapefile", "SAUEEZ_July2015.shp")) %>% 
  rename(eez_name = Name) %>% 
  # st_transform(crs = 4326) %>% # 4326
  st_transform(crs = "+proj=eck4") %>% # for tbular plot
  st_simplify(preserveTopology = TRUE, dTolerance = 0.1) %>% 
  clean_names()

@@

World_map <- rnaturalearth::ne_countries(scale = 'small', returnclass = c("sf")) %>%
  clean_names() %>% 
  select(iso_a3,sovereignt,sov_a3,name,name_long,region_wb,continent,geometry) %>% 
  st_transform(crs = "+proj=eck4") %>%
  # st_transform(crs = 4326) %>% # 4326
  mutate(iso_a3 = ifelse(sovereignt == "Norway","NOR",
                         ifelse(name == "France","FRA",
                                iso_a3)
                         )
         ) %>% 
    left_join(World_map_dat,
            by = "iso_a3")

@@

# ggplot(Eez_centroid_sf) +
#   geom_sf() +
#   geom_sf(data = World_map, aes(), fill = "grey") +
#   geom_sf(data = World_eez_sf, aes(), fill = "white")

@@

### Splitted Figure 3 for supplements

Note this chunk needs the previous one to be ran up to the forloop

```{r supplement_figure_splitted}

  # Value Map
  World_map_part <- World_map_nemer %>% 
  filter(
    tresh ==  "tresh_two",
    variable == "value"
  )

  # ToE Map 
  toe_map_data <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == "tresh_two",
           metric == "mean_yr")%>% 
sf::st_transform(crs = "+proj=eck4")

  no_toe_eez <- World_eez_sf %>% 
    filter(eez_name %in% Neighbours$eez_name, # Filter EEZs without Transboundary spp
           !eez_name %in% toe_map_data$eez_name) %>%  # Filter EEZs with ToE stocks
    rbind(russia_churchil)%>% 
sf::st_transform(crs = "+proj=eck4") %>% 
    mutate(value = NA)

  no_toe_land <- World_map %>% 
    filter(name %in% Neighbours$eez_name, # Filter EEZs without Transboundary spp
           !name %in% World_map_part$name)%>% 
sf::st_transform(crs = "+proj=eck4") %>%   # Filter EEZs with ToE stocks 
    mutate(value = NA)

  # Grey land
grey_land <- World_map %>% 
  # filter(is.na(fishing_entity_id)) %>% 
  filter(!sovereignt %in% c("Antarctica"))

  # Inlcude the participation of species

    #   geom_sf(data = no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    #   geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +

eez_map <- ggplot(toe_map_data) +
  geom_sf(aes(fill = value), # for 2000 to 2100),
          color =  "white",
          size = 0.1
  ) +
  geom_sf(data = grey_land, aes(),
          fill = "grey50", 
          color =  "white",
          size = 0.1) +
  geom_sf(data = no_toe_eez, aes(fill = as.numeric(value)),
          color =  "white",
          size = 0.1) +
  scale_fill_viridis("Average year of range shift",
                     limits = c(2000,2100),
                     breaks = seq(2000,2100,25),
                     labels = seq(2000,2100,25),
                     direction = -1,
                     na.value = "lightblue"
  ) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(legend.key.width = unit(3, "line")) +
  guides(
    fill=guide_colorbar(title.position="top", 
                        title.hjust =0.5)
  )

land_map <- ggplot(World_map_part) +
  geom_sf(aes(fill = participation-2000),
          color =  "white",
          size = 0.1
  ) +
  geom_sf(data = no_toe_land, aes(fill = as.numeric(value)),
          color =  "white",
          size = 0.1) +
  scale_fill_viridis("Transboundary fish revenue (%)",
                     limits = c(0,100),
                     breaks = seq(0,100,25),
                     labels = seq(0,100,25),
                     direction = 1,
                     na.value = "lightblue",
                     option = "A"
  ) +
  my_ggtheme_m(leg_pos = "bottom") +
  theme(legend.key.width = unit(3, "line")) +
  guides(
    fill=guide_colorbar(title.position="top", 
                        title.hjust =0.5)
  )

# ggsave(
#   plot = land_map,
#   width = 8,
#   height = 6,
#   units = "in",
#   filename = "./Figures/eez_map_supp.png"
# )

  p <- ggdraw() +
    draw_plot(eez_map, x = 0, y = 0.5, width = 1, height = 0.5) +
    # Regional boxplot
    draw_plot(land_map, x = 0, y = 0, width = 1, height = 0.5) +
    # Labels
    draw_plot_label(label = c("A", "B"), 
                    size = 20,
                    x = c(0, 0), 
                    y = c(0.98, 0.46)
    ) + 
  theme(plot.background = element_rect(fill="white", color = NA))

  save_plot(
      "./Figures/FigSplitSX.png",
    p,
    base_height = 10,
    base_width = 10
  )

@@

data_ready_plot <- data_ready_plot %>% 
  mutate(
    per_early = ifelse(per_early_plot >= 50,50,per_early_plot),
    per_mid = ifelse(per_mid_plot >= 50,50,per_mid_plot)) %>% 
  gather("time_step","percentage",per_early,per_mid)

# SELECT A TIME STEP
# time_toplot <- "per_mid"
time_toplot <- "per_early"

# ----------------------------- #

sf_ready_plot <- data_ready_plot %>% 
  filter(time_step == time_toplot) %>% 
  st_as_sf(coords = c("lon", "lat")) %>% 
  st_set_crs(4326) %>% # to match shapefiles
  st_transform(crs = "+proj=eck4")

# Get arrow data
arrows_data <- as.data.frame(st_coordinates(st_cast(sf_ready_plot,"POINT")$geometry)) %>% 
  bind_cols(data_ready_plot %>% 
              filter(time_step == time_toplot)
            )

# Get point data
point_data <- path_data %>% 
  gather("time_step","percentage",per_early:per_mid) %>% 
  filter(time_step == time_toplot,
    percentage <= 0) %>% 
  st_as_sf(
    coords = c("start_lon", "start_lat")
  ) %>% 
  select(source,target,geometry) %>% 
  st_set_crs(4326) %>% 
  st_transform(crs = "+proj=eck4")

@@

# Estimate the percentage changing
n_taxa_data <- Prop_results %>% 
  filter(variable == "n_spp") %>%
  select(eez_name,early,mid) %>% 
  left_join(n_trans_eez) %>% 
  # mutate(per = (early/n_trans)*100) %>% 
  mutate_at(vars(early,mid),
            .funs = ~(./n_trans)*100) %>% 
  rename(sf_eez_name = eez_name) %>% 
  left_join(Matching_names) %>% 
  select(sau_fishing_entity,fishing_entity_id,early,mid) %>% 
  gather("time_step","avrg_spp_per",early:mid) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,time_step) %>%
  summarise(avrg_spp_per = mean(avrg_spp_per,na.rm=T)) %>% 
  mutate(time_step = ifelse(time_step == "early","per_early","per_mid")) %>%
  mutate(avrg_spp_per_100 = avrg_spp_per,
    avrg_spp_per = ifelse(avrg_spp_per > 50,50,avrg_spp_per)) %>% 
  filter(time_step == time_toplot)

@@

# Plot
p <-
  ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
  geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
  geom_sf(data = subset(sf_ready_plot, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
  my_ggtheme_m(leg_pos = "bottom") +
    geom_path(data = subset(arrows_data, percentage >= 0),
              aes(X, Y,
                  group = group,
                  col = percentage
              ),
              size = 1,
              arrow = arrow(length = unit(0.01, "npc"),
                            ends = "first"),
              show.legend = NA) +
  my_ggtheme_m(leg_pos = "bottom") +
  scale_color_gradientn(name= "Changes in catch proportion \nand changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(sf_ready_plot$percentage,na.rm=T)),
                        breaks = seq(0,max(sf_ready_plot$percentage,na.rm=T),10),
                        labels = c(seq(0,max(sf_ready_plot$percentage-10,na.rm=T),10),">50")
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion \nand changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(sf_ready_plot$percentage,na.rm=T)),
                        breaks = seq(0,max(sf_ready_plot$percentage,na.rm=T),10),
                        labels = c(seq(0,max(sf_ready_plot$percentage-10,na.rm=T),10),">50")
  )

name <- paste0("./Figures/ssr_",time_toplot,".png")
# Save figure
ggsave(plot =  p,
       name,
       width = 10,
       height = 5,
       units = "in")

  Lat_am_data <- sf_ready_plot %>% 
    filter(source %in% Lat_am_eez$sf_eez_name)

  Lat_am_paths <- sf_ready_plot %>% 
    filter(source %in% Lat_am_eez$sf_eez_name,
           objective %in% Lat_am_eez$sf_eez_name)

  Lat_am_points <- point_data %>% 
    filter(source %in% Lat_am_eez$sf_eez_name,
           target %in% Lat_am_eez$sf_eez_name)

  Lat_am_map <- ggplot() +
    geom_sf(data = Lat_am_eez, size = 0.1, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time_toplot),
            aes(fill = avrg_spp_per),
            size = 0.1,col = "white") +
    geom_sf(data = Lat_am_points, aes(), color = "grey90") +
  my_ggtheme_m(leg_pos = "bottom") +
    geom_path(data = subset(Lat_am_paths, percentage > 0),
              aes(X, Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 1,
              arrow = arrow(length = unit(0.05, "npc"),
                            ends = "first"),
              show.legend = NA) +
    coord_sf(xlim = c(-100, -55),ylim = c(9, 30)) + 
    labs(x = "", y = "") +
    scale_x_continuous(breaks = seq(-100,60,10)) +
    scale_y_continuous(breaks = seq(10,30,10)) +
    my_ggtheme_m(leg_pos = "bottom") +
    theme(legend.position = "",
          panel.background = element_rect(fill = "white", color = "white"),
          panel.grid.major =  element_line(color = "white")
    ) +
    scale_colour_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Lat_am_data$percentage)),
      breaks = seq(0,max(Lat_am_data$percentage),10),
      # option="magma",
      # direction = -1
    )+
    scale_fill_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Lat_am_data$percentage)),
      breaks = seq(0,max(Lat_am_data$percentage),10),
      # option="magma",
      # direction = -1
    )

  ggsave(plot =  Lat_am_map,
       "test.png",
       width = 10,
       height = 5,
       units = "in")

### 2021-11-17 Scripts/responses_rev_gcb.Rmd
Created splitted figure 3 for rev.2

  - **Response:**  **NOTE: I do not (fully) agree with this comment, Do you think we can counter-argue it? (We had the same type of plot in the Sci. Rep. paper). Yes, the figure is complex, but I do not think having different color scales will make it any less complex. I actually think it will make it even harder to read.**

@@

  - Fig. 3 legend, *B) Year of shared distribution shifts by UN sub-regions. Points color coded by the median year for all shifting stocks in the region.*

>>>>

  - **Response:** We understand the reviewer’s concern with the complexity of our figure. However, after some tryouts, we concluded that having different color scales does not make it any less complex. Thus, We have made an extra effort to describe it as clearly as possible in the figure legend (see below). In addition, we have split up the land and polygons into two maps and include them in the supplemental figures (See supplement FX).

@@

  - Fig. 3 legend, - *Year of change in the shared distribution of 4,119 transboundary stocks. A) Land polygons show the contribution of shifting stocks to a country or territory's total fishing revenue from transboundary stocks. Exclusive Economic Zone polygons display average year of range shifts within them (Note that the year scale goes from end of the century to recently). Warm colors are indicative of an early shift and high fishing revenue contribution from transboundary stocks while cold colors represent a later shift and low fishing revenue. EEZs with no distributional shift between 2006 and 2100 are represented in pale blue. See Figure SXX for a detached version. B) Year of shared distribution shifts by UN sub-regions. Points color coded by the median year for all shifting stocks in the region reflecting the Kruskal-Wallis test. Horizontal dashed line represents the year by which countries have committed to reach full implementation of the 2030 Agenda. N = North, S = South, W = West and E = East. Ltn. Ame. and the Car. = Latin America and the Caribbean. Aus and New Z. = Australia and New Zealand.*
